Generating Simulated Data

### 2021-04-29 docs/SimData.Rmd
WIP survey and fishery dat in Gavin's format

This function is below, but with only 5 bins I don't likw how it works, allocating more smaller bins to the smallest sizes that we don't observe and aggregating many lengths into one large bin. Therefore the simplest approach is to have equal sized bins (max observed length/desired number of bins). We will try this for the length comps.

@@

>>>>

This function is below, but with only 5 bins I don't like how it works, allocating more smaller bins to the smallest sizes that we don't observe and aggregating many lengths into one large bin. Therefore the simplest approach is to have equal sized bins (max observed length/desired number of bins). We will try this for the length comps.

@@

Survey and catch datasets in Gavin's suggested format (all surveys together, all fleets together):

```{r svcatchalt, eval=FALSE}
#read in survey biomass data
survObsBiom <- read_savedsurvs(d.name, 'survB') #reads in all surveys

# get cvs from config files
svcon <- list.files(path=here("/simulated-data/config/"), pattern = "*survey*", full.names = TRUE)
fishcon <- list.files(path=here("/simulated-data/config/"), pattern = "*fishery*", full.names = TRUE)

omlist_ss <- NOBAom_ms
source(here("/simulated-data/config/omdimensions.R"))

svcvlook <- tibble()
for(c in 1:length(svcon)){
  source(svcon[c])
  surv_cv_n <- surv_cv %>% 
    mutate(survey=survey.name)
  svcvlook <- bind_rows(svcvlook, surv_cv_n)
}

fcvlook <- tibble()
for(c in 1:length(fishcon)){
  source(fishcon[c])
  fish_cv_n <- fish_cv %>%
    mutate(fishery=fishery.name)
  fcvlook <- bind_rows(fcvlook, fish_cv_n)
}

allsvbio <- tibble()

#multiple surveys named in list object, use as filename
for(s in names(survObsBiom)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svbio <- survObsBiom[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, year, atoutput) %>%
    dplyr::rename(biomass = atoutput) %>%
    dplyr::mutate(survey = s,
                  CV = 0.2) %>% #placeholder, can get actual value used to generate from config files
    dplyr::select(survey, year, species, everything()) %>%
    dplyr::arrange(survey, species, year)

  allsvbio <- bind_rows(allsvbio, svbio)
}
write_csv(allsvbio, paste0(o.name,"observation_biomass_NOBA_allsurvs.csv"))
